Should I Airbnb My Property: Analytic Code Explanation

### 2017-03-09 abbDataAnalysis_Script.Rmd
reorg:  revdens

---
title: "Abb Analysis"
author: "Andy Krause and Gideon Aschwanden"
date: "February 5, 2017"
output: html_document
---

@@

### Preliminary Commands

@@

@@

Next, we source the necessary custom code files for the analysis.

@@

@@

State gives energy costs at 330 (apt) to 520 (house).  For 2 person in apt that works out to 5 per person per day.  For house of 4 that works out to about 4 per person per day.

@@

  str.data$str.act.revenue <- ((str.data$bookings * str.data$med.rate) - 
                                 (str.data$bookings * str.data$avg.guests *
                                    str.data$cpppd))

@@

  str.data$str.ext.revenue <- ((str.data$bookings * str.data$extr.par *
                                  str.data$med.rate) - 
                                 (str.data$bookings * str.data$avg.guests * 
                                    str.data$cpppd * str.data$extr.par))
  # 
  str.data$occ.rate <- 1 - (str.data$block.rate + str.data$avail.rate)

@@

#### Compute revenue densities

  stra.rev <- str.data[,c('bedrooms', 'str.ext.revenue')]
  stra.rev$tenure <- 'Short-Term (Actual)   '
  names(stra.rev)[2] <- 'revenue'
  strp.rev <- str.data[,c('bedrooms', 'str.pot.revenue')]
  strp.rev$tenure <- 'Short-Term (potential)   '
  names(strp.rev)[2] <- 'revenue'
  ltr.rev <- ltr.data[,c('bedrooms', 'ltr.revenue')]
  ltr.rev$tenure <- 'Long-Term   '
  names(ltr.rev)[2] <- 'revenue'
  revdens.data <- rbind(stra.rev, strp.rev, ltr.rev)

  ggplot(revdens.data, aes(x=revenue, fill=tenure, color=tenure)) +
    geom_density(alpha=.5) +
    scale_fill_manual(values=c(ltr.col, abb.col[2], str.col)) +
    scale_color_manual(values=c(ltr.col, abb.col[2], str.col)) +
    #ggtitle('Annual Revenues by Tenure Type') +
    xlab('\nAnnual Revenue') +
    scale_x_continuous(breaks=c(seq(0,60000, by=20000)),
                       labels=c('$0', '$20k', '$40k', '$60k'))+
    theme(legend.position='none',
          legend.title = element_blank(),
          plot.title = element_text(hjust = 0.5),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.title.y=element_blank()) +
    coord_cartesian(xlim=c(0, 70000)) +
    facet_wrap(~tenure)

@@

We then employ a custom function to cross impute rates and rents for the two datasets.  The 'clip.field' is a spatial fixed effects that add spatial recognition to the models.

  imp.data <- imputeLtrRents(ltr.df=ltr.data, 
                               str.df=str.data, 
                               mod.spec=ltr.mod.spec,
                               match.factor='suburb')

From the imputed results, we extract the base data (with imputed values) as well as the model summaries.

  # Extract out DFs (only those that imputed)
  str.glob <- merge(str.data, imp.data$imp.rent, by='property.id')

Next we cross impute days on market and occupancy rates.

  # Apply dom to abb
  str.glob$imp.dom <- imputeDOM(str.glob, ltr.data, calc.type='median')

With the cross-imputed DOMs and occupancy rates we now make the cross-tenure imputations of revenues and add them back to the original datasets.

  str.glob$ltr.imp.revenue <- str.glob$imp.rent * (52 - str.glob$imp.dom / 7)

Next, we compare the revenues from the two and extract the new datasets.

  comp.revs <- compareRevenues(str.glob)

  str.glob <- merge(str.glob, comp.revs, by='property.id')

@@

 str.data.ic <- abbImputeCompare(str.df=str.data,
                                 ltr.df=ltr.data,
                                 mod.spec=ltr.mod.spec,
                                 match.factor='suburb',
                                 split.field='tbg',
                                 verbose=TRUE)

@@

>>>>

---
title: "Should I Airbnb My Property: Analytic Code Explanation"
author: "Andy Krause and Gideon Aschwanden"
date: "March 10, 2017"
output: html_document
---

@@

This document describes all of the code used to the generate the output included in the 'Should I Airbnb my Property' study.  Additional analysis that were not included in the final report are also found within this document.  This analysis uses the output from the **abbDataClean_Script.rmd** file found in the same online repository. 
### Preliminary Commands

We begin by loading the libraries necessary to do this analysis.

@@

We then set the paths to the data, code and figures, based on the user of the document.  We also set a variable indicating whether or not we are working offline.

@@

Next, we source the necessary custom code files for the analysis.  We also set a few options here.

@@

We load the workspace from the data clean script that includes the prepared data objects.

@@

### Calculating Net Revenues

We begin the analysis by calculating the net revenues for the short term data.  We calculate three types of net revenues, Observed, Extrapolated (Actual) and Potential. The difference are described more fully in the writeup.

Before we start, we estimate two figures necessary to determine utility costs: 1) Costs per person per day (cpppd) and the average number of guests per bedroom.The State of Victoria gives energy costs at \$330 (apartment) to \$520 (house).  For 2 persons in an apartment that works out to \$5 per person per day.  For a house of 4 persons that works out to about \$4 per person per day. We use a mid point value of \$4.50 per person per day.  We use an estimate of 1.5 persons per bedroom in each unit.

```{r utility_estimates, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

@@

```{r obs_revenues, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

  str.data$str.obs.revenue <- ((str.data$bookings * str.data$med.rate) - 
                                 (str.data$bookings * str.data$avg.guests *
                                    str.data$cpppd))

```{r act_revenues, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

@@

  str.data$str.act.revenue <- ((str.data$bookings * str.data$extr.par *
                                  str.data$med.rate) - 
                                 (str.data$bookings * str.data$avg.guests * 
                                    str.data$cpppd * str.data$extr.par))
```

```{r pot_revenues, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

  str.data$occ.rate <- 1 - (str.data$block.rate + str.data$avail.rate)

@@

#### Compare Revenue Distributions

@@

<!-- We then employ a custom function to cross impute rates and rents for the two datasets.  The 'clip.field' is a spatial fixed effects that add spatial recognition to the models.  -->

<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->

<!--   imp.data <- imputeLtrRents(ltr.df=ltr.data,  -->
<!--                                str.df=str.data,  -->
<!--                                mod.spec=ltr.mod.spec, -->
<!--                                match.factor='suburb') -->

<!-- ``` -->

<!-- From the imputed results, we extract the base data (with imputed values) as well as the model summaries.  -->

<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->

<!--   # Extract out DFs (only those that imputed) -->
<!--   str.glob <- merge(str.data, imp.data$imp.rent, by='property.id') -->

<!-- ``` -->

<!-- Next we cross impute days on market and occupancy rates. -->

<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->

<!--   # Apply dom to abb -->
<!--   str.glob$imp.dom <- imputeDOM(str.glob, ltr.data, calc.type='median') -->

<!-- ``` -->

<!-- With the cross-imputed DOMs and occupancy rates we now make the cross-tenure imputations of revenues and add them back to the original datasets.  -->

<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->

<!--   str.glob$ltr.imp.revenue <- str.glob$imp.rent * (52 - str.glob$imp.dom / 7) -->

<!-- ``` -->

<!-- Next, we compare the revenues from the two and extract the new datasets. -->

<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->

<!--   comp.revs <- compareRevenues(str.glob) -->

<!--   str.glob <- merge(str.glob, comp.revs, by='property.id') -->

<!-- ``` -->

@@

 str.data.ic <- abbImputeCompare(str.df=str.data,
                                 ltr.df=ltr.data,
                                 mod.spec=ltr.mod.spec,
                                 match.factor='suburb',
                                 split.field='tbg',
                                 verbose=FALSE)

Having calculated the revenues, both short-term and long-term imputed, we now compare the actual (extr), potential and imputed long-term revenue distributions for the short term properties

  buildRevDensPlot(str.data.ic,
                   rev.cols=c(ltr.col, abb.col[2], str.col))

@@

### Sensitivity
